DINO Methods for Style Transfer

### 2022-04-19 paper/Paper.tex
experiments ABC qualitative analysis

\usepackage[final]{paper_neurips_2021}

@@

\subsection{Qualitative Evaluation}

>>>>

\usepackage[preprint]{neurips_2021}

@@

\subsection{Qualitative Evaluation}
In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image. But in both cases, certain details of the objects depicted in the content image are lost. For experiment A, we can see both the content and style losses decrease over time. Meanwhile, experiment B has a decrease style loss but its content loss first decreases and then increases before oscilating and staying overall the same.

Experiment C failed to learn style transfer. At the beginning of the training, it renders each content image with a color that roughly matches the style image, but over time, it started to copy the content image while completely ignoring the style image. After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are. As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.
